### 2019-08-27 paper/paper.tex
paper updates

\begin{lstlisting}[language = Julia]
fname = joinpath(dirname(pathof(TSML)),
   "../data/testdata.csv")
csvfilter = DataReader(Dict(
   :filename=>fname,
   :dateformat=>"dd/mm/yyyy HH:MM"))
valgator = DateValgator(Dict(
   :dateinterval=>Dates.Hour(1)))
valnner = DateValNNer(Dict(
   :dateinterval=>Dates.Hour(1)))
stfier = Statifier(Dict(:processmissing=>true))
\end{lstlisting}

@@

@@

The result now indicates \emph{NaN} for all missing data statistics column because the set 
of missing blocks count is now empty.

>>>>

\begin{lstlisting}[language = Julia]
fname = joinpath(dirname(pathof(TSML)),
   "../data/testdata.csv")
csvfilter = CSVDateValReader(Dict(
   :filename=>fname,
   :dateformat=>"dd/mm/yyyy HH:MM"))
valgator = DateValgator(Dict(
   :dateinterval=>Dates.Hour(1)))
valnner = DateValNNer(Dict(
   :dateinterval=>Dates.Hour(1)))
stfier = Statifier(Dict(:processmissing=>true))
\end{lstlisting}

@@

\begin{figure}[htbp]
   \centering
   \includegraphics[width=\columnwidth]{stat1.png} % requires the graphicx package
   \vskip 2pt
      \includegraphics[width=\columnwidth]{stat2.png} % requires the graphicx package
   \caption{Data Quality Statistics. Column names starting with `b` refer to statistics of contiguous blocks of missing data.}
   \label{fig:dataquality}
\end{figure}

@@

\begin{figure}[htbp]
   \centering
   \includegraphics[width=\columnwidth]{imputed1.png} % requires the graphicx package
   \vskip 2pt
      \includegraphics[width=\columnwidth]{imputed2.png} % requires the graphicx package
   \caption{Statistics after Imputation. All statistics for blocks of missing data indicate NaN to indicate the stats of empty set. This implies that all missing blocks are imputed.}
   \label{fig:imputation}
\end{figure}

The result in Fig.~\ref{fig:imputation} now indicates \emph{NaN} for all missing data statistics column because the set 
of missing blocks count is now empty.

\vskip 3pt

We can also visualise our time series data using the \emph{plotter} filter instead of the \emph{statifier} as show below:

\begin{lstlisting}
pltr=Plotter(Dict(:interactive => true))
plpipeline = Pipeline(Dict(
   :transformers => [csvfilter, valgator, pltr]))
fit!(plpipeline)
myplot = transform!(plpipeline)
\end{lstlisting}

\begin{figure}[htbp]
   \centering
   \includegraphics[width=\columnwidth]{mplot.png} % requires the graphicx package
   \caption{example caption}
   \label{fig:example}
\end{figure}
